\documentclass{article}
\usepackage{fullpage,color}
\usepackage{amsmath,amssymb,amsthm,enumitem,cancel,verbatim}
\begin{document}

Given a failure detection delay (window) of $W$ seconds, my first formulation
of wifi failure penalty calculated at time $t$ was:
\begin{equation*}
TotalPenalty(t) = W * Pr(X < t + W | X \ge t)
\end{equation*}
or, the failover delay times the probability that the failure detection window
at the end of the current wifi session overlaps with the current transfer.
Problem: the failure penalty isn't the same for every point in the failure window.
\begin{itemize}
\item If the failure is observed IMMEDIATELY after the decision is made, 
  the penalty is zero.
\item If the failure occurs now and isn't observed until the full failure window
  passes, the penalty is $W$ (window length).
\end{itemize}
If the failure window is $W$ seconds, the current time is $t$, and the failure 
occurs at time $x \ge t$, then the penalty is simply:
\begin{equation*}
  Penalty(t, x) = \left\{
  \begin{array}{lr}
    x - t & : x < t + W\\
    0     & : x \ge t + W
  \end{array}
  \right.
\end{equation*}

This means that the penalty should be expressed as an integral over the entire
failure window, rather than just a constant multiplied by the probability that
the current session length lies in the failure window.  Thus, the wifi failure 
penalty as a function of the current time $t$ is:

\begin{align*}
TotalPenalty(t) & = \int_t^{t+W}{Penalty(t, x) * Pr(X = x | X \ge t) dx} &&  & \\
% & = \int_t^{t+W}{Penalty(t, x) * \frac{Pr(X = x \land X \ge t)}{Pr(X \ge t)} dx} && \mbox{Conditional probability definition.} & \\ 
& = \int_t^{t+W}{(x - t) * Pr(X = x | X \ge t) dx} &&  & \\
& = \int_t^{t+W}{x * Pr(X = x | X \ge t) dx} - t \int_t^{t+W}{Pr(X = x | X \ge t) dx} &&  & \\
\end{align*}
I can use the truncated distribution formulation here to pull out some constants and 
simplify the remainder of this.
\begin{align*}
Pr(X = x | X \ge t) & = \frac{Pr(X = x)}{1 - F(t)} && \mbox{as long as $x \ge t$; zero otherwise} & \\
\end{align*}
where $F(x)$ is the CDF.  Using this with the previous formula, we have
\begin{align*}
& = \int_t^{t+W}{x * \frac{Pr(X = x)}{1 - F(t)} dx} -
  t \int_t^{t+W}{\frac{Pr(X = x)}{1 - F(t)} dx} && \mbox{Truncated distribution substitution} & \\
& = \frac{1}{1 - F(t)}\left[\int_t^{t+W}{x * Pr(X = x) dx} -
  t \int_t^{t+W}{Pr(X = x) dx}\right] &&  & \\
& = \frac{1}{1 - F(t)}\left[\textcolor{red}{\int_t^{t+W}{x * Pr(X = x) dx}} -
  t (F(t+W) - F(t))\right] &&  & \\
\end{align*}
...aaaand stuck again. Closer, I think, but I still have to
calculate an integral that looks the expected value, but over an interval.

\begin{comment}
Actually, what about this...
\begin{align*}
  \int_t^{t+W}{x * Pr(X = x) dx}
  & = \int_t^{\infty}{x * Pr(X = x) dx} - \int_{t+W}^{\infty}{x * Pr(X = x) dx}
  & =
% ...not sure where I was going with this.
\end{align*}
\end{comment}

\begin{comment}
Since I know how to integrate the conditional probability using the CDF, I'll use 
integration by parts to simplify the rest of the integration.
\begin{align*}
          u  & = x \\
          dv & = \frac{Pr(X = x \land X \ge t)}{1 - F(t)} dx \\
  \int{u dv} & = u v - \int{v du} \\
          du & = 1 dx \\
           v & = \int{\frac{Pr(X = x \land X \ge t)}{1 - F(t)} dx} \\
             & = \frac{F(x) - F(t)}{1 - F(t)} \\
\end{align*}
Then, using the formulation of integration by parts:
\begin{align*}
  \int{u dv} & = u v - \int{v du} \\
             & = x \frac{F(x) - F(t)}{1 - F(t)}\biggr\rvert_t^{t+W} - \int_t^{t+W}{\frac{F(x) - F(t)}{1 - F(t)} dx} \\
             & = \frac{1}{1 - F(t)} \left[x (F(x) - F(t))\biggr\rvert_t^{t+W} - \int_t^{t+W}{F(x) dx} - F(t)\right] \\
  & = \frac{1}{1 - F(t)} \left[(t+W) (F(t+W) - F(t)) - \cancelto{0}{t (F(t) - F(t))} - \int_t^{t+W}{F(x) dx} - F(t)\right] \\
\end{align*}
\end{comment}

\end{document}
